\documentclass[12pt]{article}

\begin{document}

\noindent Sam Hart \\
Noah Santer \\
CS 292 \\
Professor Dooley \\
\today \\

\section{Requirements}

\begin{itemize}
    \item Poker Squares shall be a game that shall run on the target system.\footnote[1]{Which is clearly a Unix like OS and not Windows.}
    \item Poker Sqaures shall comply with the standard rules for the solitaire game "Poker Squares" as outlined in \textit{PokerSquaresRules.pdf}.
    \item Poker Squares shall have an abstract concept of a \textit{player}, and this concrete versions of this \textit{player} will control the program.
    \item Poker Squares shall have the ability to let a \textit{player} place cards and shall keep track of where they are placed on the board.
    \item Poker Squares shall \textit{understand} how to score a board configuration so that from given a board configuration it shall be able to deduce a numerical score.
    \item Poker Squares shall have both computer and human players.\footnote[2]{In iterations after the first.}
    \item Poker Squares shall allow the user to select the type of player that will play the game begins before play begins.
    \item Poker Squares shall understand how to display the board to a hypothetical human player, and shall have the ability to be adapted to multiple ways of doing so.
    \item Poker Squares shall have the ability to run multiple games in a row and calculate average scores of those games for any type of computer player.
    \item Poker Squares shall be able to generate fair and random decks that will effectively test an AI and its ability to play the game.
    \item For the first iteration of the program Human players will not be considered a necessary feature.
    \item For the first iteration, only the Flush-seeking AI and the random player will be considered necessary features.
    \item For the first iteration, a GUI will not be considered a necessary feature.
\end{itemize}

\end{document}
